Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-06-20 vesicle_code/docs/adhesion/adhesion.tex
added author contribution section
started writing about the period

We characterize the effect of the Hamaker constant and shear rate by
determining a critical Hamaker constant, $\mathcal{H}_c$, which
determines if the vesicles form a doublet or separate.  We fix the
separation distance to $\delta = 0.4$ and the vesicle reduced area to
$\Delta A = 0.9$.  In the left plot of
Figure~\ref{fig:sflow_distance}, we plot the minimum distance
between the vesicles as a function of time for various Hamaker
constants.  The red curves correspond to Hamaker constants that are too
small to bind the vesicles into a doublet, and the blue curves
correspond to Hamaker constants that are sufficiently large to form a
doublet.  Figure~\ref{fig:sflow_phase_diagram} indicates whether a
doublet with reduced area $\Delta A = 0.9$ is formed (blue) or not (red)
for a variety of shear rates, Hamaker constants, and at two different
separation distances.  The plot includes a line of best fit between the
stable and unstable regions.  Since the transition is linear, this
indicates that a dimensionless number involving the ratio of the Hamaker
constant could be used to determine if a doublet forms or not.

\begin{figure}
  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1Chi5em1_ra090.pdf}
  \caption{\label{fig:sflow_distance} {\em Left}: The distance between a
  pair of vesicles in a planar shear flow with shear rate $\chi=0.5$,
  and separation distance $\delta = 0.4$.  The different lines
  correspond to a linear spacing of Hamaker constants ranging from
  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Right}:
  \todo[inline]{frequency of the oscillation}}
\end{figure}

@@

>>>>

We characterize the effect of the Hamaker constant and shear rate by
determining a critical Hamaker constant, $\mathcal{H}_c$, which
determines if the vesicles form a doublet or separate.  We fix the
separation distance to $\delta = 0.4$ and the vesicle reduced area to
$\Delta A = 0.9$.  In the left plot of
Figure~\ref{fig:sflow_distance}, we plot the minimum distance
between the vesicles as a function of time for various Hamaker
constants.  The red curves correspond to Hamaker constants that are too
small to bind the vesicles into a doublet, and the blue curves
correspond to Hamaker constants that are sufficiently large to form a
doublet.  We also plot the time required for the doublet to make a
complete revolution at a variety of Hamaker constants and shear rates.
For a fixed Hamaker contant, as expected, the period decreases for
larger shear rates.  In addition, for a fixed shear rate, the period
decreases as the Hamaker constant increases, but the period eventually
plateaus.  More interesting, for larger shear rates, the period of the
doublet appears to be independent of the Hamaker constant.

Figure~\ref{fig:sflow_phase_diagram} indicates whether a doublet with
reduced area $\Delta A = 0.9$ is formed (blue) or not (red) for a
variety of shear rates, Hamaker constants, and at two different
separation distances.  The plot includes a line of best fit between the
stable and unstable regions.  Since the transition is linear, this
indicates that a dimensionless number involving the ratio of the Hamaker
constant could be used to determine if a doublet forms or not.

\begin{figure}
  \includegraphics[height=0.34\textwidth]{figs/shear_adR4em1Chi5em1_ra090.pdf}
  \includegraphics[height=0.34\textwidth]{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
  \caption{\label{fig:sflow_distance} {\em Left}: The distance between a
  pair of vesicles in a planar shear flow with shear rate $\chi=0.5$,
  and separation distance $\delta = 0.4$.  The different lines
  correspond to a linear spacing of Hamaker constants ranging from
  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Right}: The time
  required for a doublet to complete a single rotation.  The reduced
  area is $\Delta A = 0.90$ and the separation distance is $\delta =
  0.4$.  The different lines correspond to different shear rates.}
\end{figure}

@@

BQ and YNY contributed equally to model development, code development,
and simulations.  All authors contributed equally to writing the
manuscript.
